Topological Equivariant Artist Model for Visualization Library Architecture

### 2023-11-22 paper/main.tex
environment

Since the earliest maps \cite{friendlyBriefHistoryData2006}, a visualization has been expected to preserve the $field$ properties and $topology$ of the corresponding dataset; a \textcolor{fiber}{\textcolor{field}} \footnote{Throughout this paper, we augment the math with color to group conceptually similar objects and functions\cite{headMathAugmentationHow2022}, for example \textcolor{action}{actions} and \textcolor{action}{sets of actions}. This color coding carries through to the figures.}  is a set of values of the same type, e.g. one column of a table or the pixels of an image, and \textcolor{base}{\textcolor{topology}} is the connectivity and relative positioning of elements in a dataset \cite{wilkinsonGrammarGraphics2005}. In \autoref{fig:related-work:continuity:ktypes}, the topology is a continuous 3 dimensional surface encapsulating time and position, while the fields are date, location, station, pressure, and temperature. Our paper provides a language to express how the scatter plot, line plot, and heatmap are preserving different structural properties of the dataset, thereby generalizing Bertin's codification of how the topology of observations must match the class of representation (i.e. point , line, area) and how the variation possible in a field match the variation in the corresponding visual variable \cite{bertinSemiologyGraphicsDiagrams2011} and Mackinlay's work on how structure preservation includes preserving the mathimatical relations between elements of the same and different fields \cite{mackinlayAutomatingDesignGraphical1986}.

>>>>

Since the earliest maps \cite{friendlyBriefHistoryData2006}, a visualization has been expected to preserve the $field$ properties and $topology$ of the corresponding dataset; a \textcolor{fiber}{\textbf{field}} \footnote{Throughout this paper, we augment the math with color to group conceptually related terms\cite{headMathAugmentationHow2022}, for example \textcolor{fiber}{field} and \textcolor{fiber}{fiber}. This color coding carries through to the figures.}  is a set of values of the same type, e.g. one column of a table or the pixels of an image, and \textcolor{base}{\textcolor{topology}} is the connectivity and relative positioning of elements in a dataset \cite{wilkinsonGrammarGraphics2005}. In \autoref{fig:related-work:continuity:ktypes}, the topology is a continuous 3 dimensional surface encapsulating time and position, while the fields are date, location, station, pressure, and temperature. Our paper provides a language to express how the scatter plot, line plot, and heatmap are preserving different structural properties of the dataset, thereby generalizing Bertin's codification of how the topology of observations must match the class of representation (i.e. point , line, area) and how the variation possible in a field match the variation in the corresponding visual variable \cite{bertinSemiologyGraphicsDiagrams2011} and Mackinlay's work on how structure preservation includes preserving the mathimatical relations between elements of the same and different fields \cite{mackinlayAutomatingDesignGraphical1986}.
